---
title: "Application layouts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{layout}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
  .sourceCode + .container-fluid .row > div {
    border: 1px solid blue;
  }
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
suppressPackageStartupMessages(library(yonder))
```

### Classic sidebar and main panel

```{r, results="asis"}
container(
  columns(
    column(
      width = 4,
      p("Sidebar panel")
    ),
    column(
      width = 8,
      p("Main panel")
    )
  )
)
```

### Three column layout

```{r, result="asis"}
container(
  columns(
    column(
      p("Column 1")
    ),
    column(
      p("Column 2")
    ),
    column(
      p("Column 3")
    )
  )
)
```

### Main panel with columns below

The three panels below the main panel render in a column on small screens. Swap in `md` or `lg` for `sm` to switch to a column layout on larger screens. 

```{r, result="asis"}
container(
  columns(
    column(
      width = 12,
      p("Main panel")
    ),
    column(
      width = c(xs = 12, sm = 4),
      p("Column 1")
    ),
    column(
      width = c(xs = 12, sm = 4),
      p("Column 2")
    ),
    column(
      width = c(xs = 12, sm = 4),
      p("Column 3")
    )
  )
)
```

### Further reading

Use `display()` with `type = "flex"` and `flex()` to use flex box layout. See
https://developer.mozilla.org/en-US/docs/Web/CSS/CSS_Flexible_Box_Layout/Basic_Concepts_of_Flexbox for more information on flex box layout.

