```{r, child = "_setup.Rmd"}
```

## Dismissible alerts

With `dismissible = TRUE` you can allow the user to remove an alert. By default,
alerts are dismissible, well suited for one-time messages or warnings.

```{r}
alert(
  .style %>%
    background("primary"),
  "I'm around till you say goodbye"
)
```

## Static alerts

If you do want to keep an alert or control an alert with `renderUI()` you can
then use `dismissible = FALSE`.

```{r}
alert(
  .style %>%
    background("warning"),
  dismissible = FALSE,  # <-
  "I'm calling attention to something, forever."
)
```

## Contextual content

Alerts include a few contextual variations. Links and headings are both styled
differently inside an alert.

```{r}
alert(
  .style %>%
    background("success"),
  h5("Success!"),
  "Your results can be found",
  a(href = "#", "here")
)
```

If you want to avoid these automatic styles you can use `tags$a`, `tags$h1`,
`tags$h2`, etc.

```{r}
alert(
  .style %>%
    background("light") %>%
    border("dark"),
  tags$h6("Default heading"),
  h6("Alert heading"),
  hr(),
  tags$a(href = "#", "Default link"),
  a(href = "#", "Alert link")
)
```

Like the `a()` tag elements, yonder's `linkInput()`s also receive contextual
styling.

```{r}
alert(
  .style %>%
    background("danger"),
  h5("Problem"),
  hr(),
  linkInput(
    id = "rerun",
    label = "Click to run again"
  )
)
```
