```{r, child = "_setup.Rmd", include = FALSE}
```

## Input backgrounds

Input backgrounds will change differently according to the particular input.
Changing the background of a `buttonGroupInput()` will change the background
colors of the buttons in the group.

```{r}
buttonGroupInput(
  .style %>%
    background("info") %>%  # <-
    display("flex"),
  id = "flavors",
  choices = c("Mint", "Strawberry", "Swirl"),
  values = c("mint", "strawberry", "swirl")
)
```

Changing the background of an input is different than changing a tag
element. More is done under the hood to apply the correct background
styles. For example, changing the background of a radio or checkbox input
changes the color of the selected choices.

```{r}
radioInput(
  .style %>%
    background("warning"),
  id = "drinks",
  choices = c("Limemade", "Lemonade", "Orangeade"),
  values = c("lime", "lemon", "orange"),
  selected = "lime"
)
```

If you needed to change the entire background of an input, you can wrap the input
in a `div()` and modify its background.

```{r}
div(
  .style %>%
    padding(2) %>%
    background("dark"),  # <-
  radioInput(
    .style %>%
      font("light") %>%
      background("success"),
    id = "valid",
    choices = c("Yes", "No"),
    values = c("y", "n"),
    selected = "n"
  )
)
```
