```{r, child = "_setup.Rmd"}
```

### Getting started

```{r}
buttonInput(
  id = NULL,
  label = "Label"
)
```

### Add a little color

```{r}
buttonInput(
  .style %>%
    background("primary"),
  id = NULL,
  label = "Label"
)
```

Use the `width()` utility to adjust the size of a button.

```{r}
buttonInput(
  .style %>%
    background("danger") %>%
    width(75),  # <-
  id = NULL,
  label = "Label"
)
```

### Reactive links

```{r}
div(
  "Curabitur", linkInput(id = "link1", label = "vulputate"),
  "vestibulum lorem."
)
```

### Stretched buttons and links

Use a stretched button to make an entire card clickable.

```{r}
card(
  .style %>%
    border("primary") %>%
    font("primary"),
  header = "Product summary",
  p("Here is a summary"),
  p("This is a second paragraph"),
  footer = list(
    buttonInput(
      .style %>%
        background("primary"),
      id = "seemore",
      label = "See more",
      stretch = TRUE
    )
  )
)
```

Notice, when you hover over the card the mouse cursor changes and the button
appears hovered. The card is now passing clicks on to the button. Clicking
anywhere on the card will trigger a click on the button.

```{r}
card(
  header = "Card with stretched button",
  p("Notice when you hover over the card, the button also detects ",
    "the hover."),
  buttonInput(
    .style %>%
      background("primary"),
    id = NULL,
    label = "Label",
    stretch = TRUE
  )
)
```

### Download button

Pair a download button input with `shiny::downloadHandler()`.

```{r}
buttonInput(
  download = TRUE,  # <-
  id = NULL,
  label = "Download",
  tags$i(class = "fas fa-download")
)
```
