```{r, child = "_setup.Rmd"}
```

## Getting started

Checkbox inputs may have a single possible value.

```{r}
checkboxInput(
  id = NULL,
  choices = "Choice 1",
  selected = "Choice 1"
)
```

You may also specify multiple possible values.

```{r}
checkboxInput(
  id = NULL,
  choices = c("Choice 1", "Choice 2", "Choice 3"),
  selected = c("Choice 1", "Choice 2")
)
```

## Layout

While checkbox input choices are typically laid out vertically you can lay out
the choices horizontally with `inline = TRUE`.

```{r}
checkboxInput(
  id = NULL,
  choices = c("Choice 1", "Choice 2", "Choice 3"),
  inline = TRUE  # <-
)
```

## Switch variant

The switch input functions identical to the checkbox input with a different
appearance.

```{r}
switchInput(
  id = NULL,
  choices = c("Toggle 1", "Toggle 2", "Toggle 3"),
  selected = "Toggle 2"
)
```

## Background color

Changing the background color of a checkbox or switch input will modify the
background color of the _selected_ choices.

```{r}
checkboxInput(
  .style %>%
    background("warning"),
  id = NULL,
  choices = c("Choice 1", "Choice 2"),
  selected = c("Choice 1", "Choice 2")
)
```

```{r}
switchInput(
  .style %>%
    background("success"),
  id = NULL,
  choices = c("Toggle 1", "Toggle 2"),
  selected = "Toggle 1"
)
```

## Labelling

```{r}
formGroup(
  label = "Label",
  checkboxInput(
    id = NULL,
    choices = c("Choice 1", "Choice 2")
  ),
  help = "Help text for the input"
)
```
