```{r, child = "_setup.Rmd"}
```

## Equal width columns

```{r}
container(
  columns(
    column(
      "Aliquam erat volutpat."
    ),
    column(
      "Mauris mollis tincidunt felis."
    ),
    column(
      "Cum sociis natoque penatibus et magnis dis parturient montes,",
      "nascetur ridiculus mus."
    )
  )
)
```

## Sidebar layout

```{r}
container(
  columns(
    column(
      width = 4,  # <-
      card(
        h5("Sidebar panel")
      )
    ),
    column(
      h5("Main panel")
    )
  )
)
```

## Mobile friendly

Use the [responsive] `width` argument to make mobile friendly applications. On
extra small screens each column spans the entire width of the row. On larger
screens the columns will instead split the row width evenly.

```{r}
container(
  columns(
    column(
      width = c(xs = 12, sm = 4),
      "Mauris ac felis vel velit tristique imperdiet."
    ),
    column(
      width = c(xs = 12, sm = 4),
      "Nam vestibulum accumsan nisl."
    ),
    column(
      width = c(xs = 12, sm = 4),
      "Proin neque massa, cursus ut, gravida ut, lobortis eget, lacus."
    )
  )
)
```

## Automatic column sizing

Columns may be fit to the width of their content. Other columns in this example
will split the remaining space equally.

```{r}
container(
  columns(
    column(
      .style %>%
        background("warning")
    ),
    column(
      width = "content",
      "Cras placerat accumsan nulla. Aenean in sem ac leo mollis blandit.",
      "Nam euismod tellus id erat.",
      "Donec neque quam, dignissim in, mollis nec, sagittis eu, wisi."
    ),
    column(
      .style %>%
        background("warning")
    )
  )
)
```

Without specficiying widths the space in a row is evenly split between columns.

```{r}
container(
  columns(
    column(),
    column(),
    column(),
    column()
  )
)
```
