```{r, child = "_setup.Rmd"}
```

### Centering an element

In most modern browsers you want to horizontally center a tag element using the
flex layout. Alternatively, you can horizontally center an element using
`margin(.., right = "auto", left = "auto")`.

```{r}
div(
  .style %>%
    margin(t = 2, r = "auto", b = 2, l = "auto") %>%  # <-
    padding(3) %>%
    background("info"),
  "Nam a sapien. Integer placerat tristique nisl."
)
```

### Building an inline form

Inline form elements automatically use the flex layout providing you a means of
creating condensed sets of inputs. However, you may need to adjust the spacing
of the form's child elements.

Here is an inline form **without** any additional spacing applied.

```{r}
formInput(
  id = NULL,
  inline = TRUE,
  textInput(
    id = "name",
    placeholder = "Full name"
  ),
  groupTextInput(
    id = "username",
    left = "@@",
    placeholder = "Username"
  ),
  checkboxInput(
    id = "remember",
    choice = "Remember me"
  ),
  formSubmit("Login", "login")
)
```

Without any adjustments the layout is not great. But, **with** some styling we
can make this form sparkle. Notice we are also adjusting the default submit
button added to the form input.

```{r}
formInput(
  id = NULL,
  inline = TRUE,
  textInput(
    .style %>%
      margin(r = c(sm = 2), b = 2),  # <-
    id = "name",
    placeholder = "Full name"
  ),
  groupTextInput(
    .style %>%
      margin(r = c(sm = 2), b = 2),  # <-
    id = "username",
    left = "@@",
    placeholder = "Username"
  ) ,
  checkboxInput(
    .style  %>%
      margin(r = c(sm = 2), b = 2),  # <-
    id = "remember",
    choice = "Remember me"
  ),
  formSubmit(
    .style %>%
      margin(b = 2),
    label = "Login",
    value = "login"
  )
)
```
