---
always_allow_html: yes
output:
  github_document:
    pandoc_args: ["--wrap=preserve", "--to", "html5", "--quiet"]
---

```{r, setup, include = FALSE}
set.seed(3030)

knitr::opts_chunk$set(
  eval = TRUE,
  results = "asis"
)

# library(yonder)
devtools::load_all("..")
options(yonder.deps = FALSE)
```

```{r, title}
d3("yonder")
```

<p class="lead">
A shiny framework.
</p>

```{r, description, echo = FALSE}
p(
  class = "lead",
  "Build shiny applications with an all new set of",
  "inputs, utilties, and design tools. Click",
  linkInput(
    id = NULL,
    label = "here",
    `data-toggle` = "collapse",
    `data-target` = ".hasCopyButton"
  ),
  "to see these great new tools help build pieces of this page."
)
```

## Inputs

::: { .row }
::: { .col-md-6 .col-12 }
New inputs let you build a variety of user interfaces. Develop the best ui for
your users' needs. Whether you are building an application for personal use,
internal use, or public use an intuitive ui helps guide users through your
application.
:::
::: { .col-md-6 .col-12 }
```{r, button-group}
# button group input
div(
  .style %>%
    display("flex") %>%
    flex(justify = "center"),
  buttonGroupInput(
    .style %>%
      background("primary"),
    id = NULL,
    choices = c("Sample", "Model", "Download")
  )
)
```
:::
:::

::: { .row }
::: { .col-md-6 .col-12 }
As shiny developers we are not only developing programs and scripts for a
variety of users we are developing applications for many different devices.

Yonder's inputs are ready for both mobile and web. Once you include
:::
::: { .col-md-6 .col-12 }
```{r, list-group}
# list group input
div(
  .style %>%
    display("flex") %>%
    flex(align = "center", justify = "center"),
  card(
    .style %>%
      border("info") %>%
      background("info") %>%
      font("light"),
    header = "Learn more",
    listGroupInput(
      .style %>%
        background("info"),
      flush = TRUE,
      id = NULL,
      choices = c("About", "Our process", "Partners", "License")
    )
  )
)
```
:::
:::

## Designs

::: { .row }
::: { .col-12 }
Based on the widely used Bootstrap library, yonder provides a series of design
utilities to help prototype and produce the shiny apps you imagine.
:::
:::

::: { .row }
::: { .col-4-md .col-12 }
That control panel never has to sit on the left again.
:::
::: { .col-8-md .col-12 }
```{r}
div(
  .style %>%
    width(100) %>%
    padding(2) %>%
    display("flex") %>%
    flex(justify = "center") %>%
    border("dark", round = "all"),
  card(
    header = "Controls",
    formGroup(
      label = "Options",
      selectInput(
        id = NULL,
        choices = c("Option 1", "Option 2", "Option 3")
      )
    ),
    buttonInput(
      .style %>%
        background("primary"),
      id = NULL,
      label = "Run"
    )
  )
)
```
:::
:::

::: { .row .mt-5 }
::: { .col-12 }
```{r}
div(
  .style %>%
    width(100) %>%
    padding(2) %>%
    display("flex") %>%
    flex(justify = "end") %>%
    border("dark", round = "all"),
  dropdown(
    .style %>%
      background("secondary"),
    label = "Menu",
    h5("Controls") %>% margin(r = 3, l = 3),
    formInput(
      .style %>% padding(r = 3, l = 3),
      id = NULL,
      formGroup(
        label = "Target",
        input = textInput(
          id = NULL
        )
      ),
      formGroup(
        label = "Description",
        input = textInput(
          id = NULL
        )
      ),
      buttonInput(
        .style %>% background("primary"),
        id = NULL,
        label = "Update"
      )
    )
  )
)
```
:::
:::

::: { .row }
::: { .col-md-4 .col-12 }
Convey more.
:::
:::

::: { .row }
::: { .col-12 .d-flex .justify-content-center }

::: { .display-4 .my-3 }
... and much [more](reference/index.html)!
:::

:::
:::
